Multi-fluids for Representing Sub-filter-scale Convection

### 2020-03-31 submit2/manuscript.tex
Started revisions and responses to reviewer 2

\begin{abstract}
Multi-fluid modelling is a promising new method of representing sub
and near grid-scale convection allowing for consistent and accurate
treatment of net mass transport by convection, non-equilibrium and
turbulence. The air is partitioned into convecting and non-convecting
fluids each with their own velocity, temperature and constituents
so that separate equations of motion can be solved for each fluid,
thus representing features that cannot be resolved in a single-fluid
at coarse resolution.

This paper presents multi-fluid Boussinesq equations for representing
under resolved dry convection. We present a new model for entrainment
and detrainment based on divergence which leads to excellent representation
of the convective area fraction. Previous multi-fluid modelling of
convection has assumed that all fluids share the same pressure. We
show that this is a bad assumption and we propose and validate a model
for the pressure difference between the fluids based on divergence.

Two vertical slice test cases are used to validate the multi-fluid
model; a buoyant rising bubble and radiative convective equilibrium
are simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity. The multi-fluid model reproduces
the mean properties of the rising and falling fluids in a \change[HW]{single}{one} column. 
\end{abstract}

\section*{Plain Language Summary}
Clouds and buoyant convection are often smaller than the grid size in weather and climate prediction models but they are of central importance. Therefore their effects are parameterised -- their interactions with the larger scales are estimated based on properties of the larger scales. Convection parameterisations are a large source of error in models of the atmosphere despite decades of effort to improve them. An important assumption in most convection parameterisations is that convection moves heat and moisture upwards but not mass. This makes it much simpler to incorporate convection parameterisations into existing models. Multi-fluid modelling will enable mass transport by convection but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model. This paper provides some closures necessary for multi-fluid modelling and validation of the technique for two dimensional dry convection.

@@

\citeA{TWV+18} proposed multi-fluid modelling of convection in order
to treat non-equilibrium and net mass transport correctly and consistently
with the same numerics and physics controlling thermals, the stable
environment and downdraught dynamics. \citeA{Yano14} derived similar
equations for multiple segments and showed how this is a generalisation
of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
diffusivity mass flux'' or extended EDMF scheme also uses similar
equations but \citeA{TKP+18}
\change[HW]{didn't propose a suitable numerical method for solving the equations.}
{only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
Multi-fluids promises big improvements
in the representation of sub-grid-scale convection and unification
with the representation of turbulence, particularly at the grey zone.
However, there is a long way to go, particularly as multi-fluids requires
a dedicated model rather than being a stand alone parameterisation
for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
of the multi-fluid equations assuming two fluids that share the same
pressure (or that pressure differences are predominantly due to drag
between the fluids). \citeA{TEB19} showed that these equations (without
drag) are in fact unstable and can be stabilised by diffusion of vertical
velocity whereas \citeA{WM19} stabilised the equations with diffusion
and drag between fluids. Neither of these stabilisation techniques
are acceptable and in this paper we show that there are significant
and sustained pressure differences between the fluids (section \ref{sec:results}).

@@

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations; convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Buossinesq equations. Therefore for simplicity we focus on the
\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
\note[HW]{This is additional material until the start of 2.1}
\begin{eqnarray}
\frac{\partial \mathbf{u}}{\partial t} + \nabla\cdot(\mathbf{u}\mathbf{u})
+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
\label{eq:singleMom}
\\
\frac{\partial b}{\partial t} + \nabla\cdot(\mathbf{u}b)
 & = & \alpha\nabla^{2}b
\label{eq:singleb}
\\
\nabla\cdot\mathbf{u} & = & 0
\label{eq:singleDivFree}
\end{eqnarray}
where variables are defined in table \ref{tab:defns}.

@@

The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations. Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere and satisfy:
\begin{equation}
\frac{DI_i}{Dt}=0.
\label{eq:LagrangianLabel}
\end{equation}
Applying the conditional average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
\begin{eqnarray}
\sigma_i &=& \overline{I_i} \\
\sigma_i \mathbf{u}_i &=& \overline{I_i \mathbf{u}} \\
\sigma_i b_i &=& \overline{I_i b}
\label{eq:defineFluidFields}
\end{eqnarray}
which implies
\begin{equation}
\sum_{i}\sigma_{i}  =  1.
\label{eq:sumOne}
\end{equation}
As we are considering the Boussinesq equations we assume that variations in density only affect the buoyancy terms so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.

@@

Eqns ({eq:momFlux}) and ({eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated:
\begin{eqnarray}
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
& = &
b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt}
& = &
\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
\end{eqnarray}
where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$,

@@

\citeA{TEB19} and \citeA{WM19} assumed that each co-located fluid
shared the same pressure, leading to unstable equations that \citeA{TEB19}
stabilised using diffusion of vertical velocity and \citeA{WM19}
stabilised using mass exchanges or drag between the fluids. \citeA{TEB19}
achieved realistic results in \change[HW]{single}{one} column experiments of convective
boundary layer but the amount of diffusion needed would spoil simulations
in the free troposphere. The stabilisation used by \citeA{WM19} meant
that the two fluids tended to move as one which defeats the purpose
of using multi-fluid modelling.

@@

We will assume that pressure in each fluid is given by a parameterised
perturbation, $p_{i}$, from the total pressure, $P$:
\begin{equation}
P_{i}=P+p_{i}.
\end{equation}
\add[HW]{In order to derive a suitable form of parameterisation for $p_i$ we will first consider the} \citeA{BN86} \add{model.}

@@

The different fluids may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}.
In fact, the most buoyant air should be transferred from fluid 0 to
fluid 1 and vice versa, and the air with least downward momentum should
be transferred from 0 to 1 and vice versa. The properties of the fluids
transferred should depend on the modelling of sub-grid-scale variability
which is beyond the scope of this paper. In section \ref{sec:results}
we conditionally average high resolution solutions based on the sign
of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
Therefore the air that is transferred at the interface will have $w=0$.
For two dimensional multi-fluid simulations we assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from. Therefore
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
For buoyancy, following \citeA{TEB19}, we use:
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
\end{equation}
and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
\add[HW]{
$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<eg.>{AK67,AS74}.
}
Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is loosing mass (as demonstrated in section \ref{sec:results}).

@@

\section{Numerical Solution \label{sec:numerics}}

@@

\section{Validation Test Cases\label{sec:results}}

Two test cases are developed to tune parameters and to validate the
use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
convection. The first is transient; the standard rising bubble of
\citeA{BF02}. \remove{We aim to reproduce the vertical heat transport, the
mean velocity of the rising air, the bouyancy of the rising air and
pressure differences between two fluids in a single column two fluid
model.} The second test case is steady state with heat transfer at
the ground and uniform radiative cooling. For both test cases the
reference solution is a single-fluid solution of the two-dimensional
Boussinesq equations at high horizontal and vertical resolution. \add[HW]{This will be compared with the two-fluid model run using one column. We aim to reproduce the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column two-fluid model.}

@@

Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
Three values of $\gamma$ are tested. $\gamma$ is set from equation
(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
radius and a buoyancy scale equal to the initial maximum buoyancy
to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
the velocity profile too smooth and the updraught too weak so the
bubble does not rise enough. It is reasonable to consider smaller
values of $\gamma$ because the buoyancy does not retain its initial
maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
leads to the leading edge of the bubble rising too quickly. Smaller
values of $\gamma$ leave a discontinuity in the updraught velocity
at the leading edge of the bubble and larger values of $\gamma$ reduce
the velocity further, meaning that the bubble does not rise enough
(not shown). None of the values of $\gamma$ reproduce the peak updraught
velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
meaning that the bubble rise and $\sigma_{1}$ are approximately correct
and pressure increases above the centre of the bubble are realisitic.
The large low pressure at the bottom of the bubble is not reproduced.
This is located at the lobes of the highest buoyancy in the resolved
simulation (figure \ref{fig:bubble}). It would be tempting to model
this by assuming hydrostatic pressure or the Bernouilli equation,
but these are both forms of the momentum equation which is used to
calculate the velocity and so cannot also be used to model the pressure.

The results in the top row of figure \ref{fig:multiFluidSingleColumn}
use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
drag slows the updraughts without increasing the mixing between the
fluids which makes the solutions less like the resolved simulations.
Although drag is known to be an important term in the momentum equations
for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related
to mixing with downdraught air which is accounted for in the entrainment
term of the momentum equation. So adding a separate term from drag
risks double counting and slows the plume too much.

@@

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
This combination produces smooth solutions but the updraught is too
weak and too much is entrained into fluid 1. Using this entrainment,
the updraught will entrain more and more air until $\sigma_{1}=1$.
The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
entrainment and detrainment for this test case using conditional averaging
based on $w$.

Two alternative models for estimating the buoyancy of the fluid transferred
between updraught and downdraught have been tested. The results in
the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraught),
the mean buoyancy of fluid one increases. This leads to very high
buoyancy in fluid one which is not present in the resolved simulation.
The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. This again leads to very
large buoyancy in fluid one and also negative buoyancy in fluid zero
which should not occur for this test case. These simple models reinforce
the idea that the buoyancy of the fluid transferred should depend
on knowledge of sub-grid-scale variability of $b$ within each fluid
\textendash{} these simple assumptions can lead to unrealistic behaviour.
The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
fluid transferred takes the mean properties with it.

This section has demonstrated the value of using \change[HW]{single}{one} column,
multi-fluid model to simulate a buoyant rising bubble with a single
updraught fluid and a single downdraught fluid. Transfers between
the fluids have been successfully modelled using entrainment set by
divergence giving realistic updraught fractions. Entrainment calculated
as the reciprocal of plume width was not successful. The pressure
difference between the fluids has also been represented by divergence
with a coefficient close to that expected from dimensional analysis.
Including drag between the fluids did not improve simulations. Two
models of transferring non-mean properties between fluids were tested
but neither was plausible. There are clearly discrepancies between
the single-fluid resolved rising bubble and the two fluid \change[HW]{single}{one} column
rising bubble but we do not want to over fit the multi-fluid model
to one, dry, two dimensional test case.

@@

This test case is designed to have strong updraughts in narrow plumes
and weak descent elsewhere to mimic atmospheric convection but without
the complication of moisture, phase changes and three spatial dimensions.
A snapshot of the buoyancy, vertical velocity and pressure of the
radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
updraughts. The buoyant air at the ground rises in narrow plumes,
accelerating due to buoyancy and pressure gradients then decelerating
due to pressure gradients before reaching the top. The plumes spread
out and the sinking air is a mixture of warm and cold with similar
pressure gradients in the rising and falling air, accelerating then
decelerating the flow so as to maintain continuity.

@@

This paper presents solutions of the multi-fluid Boussinesq equations
for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution. Two test cases are used to validate
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are conditionally averaged based on the sign
of vertical velocity ($w$) in order to create rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.

>>>>

\begin{abstract}
Multi-fluid modelling is a promising new method of representing sub
and near grid-scale convection allowing for consistent and accurate
treatment of net mass transport by convection \add[HW]{and of} non-equilibrium \add[HW]{dynamics} \remove[HW]{and turbulence}. The air is partitioned into \change[HW]{convecting and non-convecting}{two or more}
fluids \add[HW]{which may represent, for example, updrafts and the stable environment.} \change[HW]{each with their}{Each fluid has its} own velocity, temperature and constituents
with separate equations of motion. \remove[HW]{can be solved for each fluid,
thus representing features that cannot be resolved in a single-fluid
at coarse resolution.}

This paper presents \change[HW]{multi}{two}-fluid Boussinesq equations for representing
under-resolved dry convection \add[HW]{with sinking and $w=0$ air in fluid 0 and rising air in fluid 1}. We present a \remove[HW]{new} model for entrainment
and detrainment based on divergence which leads to excellent representation
of the convective area fraction. Previous multi-fluid modelling of
convection has assumed that \change[HW]{all}{both} fluids share the same pressure. \change[HW]{We show that this is}{This is shown to be} a bad assumption and \remove[HW]{we propose and validate} a model
for the pressure difference between the fluids based on divergence \add[HW]{is presented}.

Two vertical slice test cases are used to \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid
model; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
are simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity. The \change[HW]{multi}{two}-fluid model reproduces
the mean properties of the rising and falling fluids in \change[HW]{a single}{one} column. 
\end{abstract}

\section*{Plain Language Summary}
Clouds and buoyant convection are often smaller than the grid size in weather and climate prediction models but they are of central importance. Therefore their effects are parameterised -- their interactions with the larger scales are estimated based on properties of the larger scales. Convection parameterisations are a large source of error in models of the atmosphere despite decades of effort to improve them. An important assumption in most convection parameterisations is that convection moves heat and moisture upwards but not mass. This makes it much simpler to incorporate convection parameterisations into existing models. Multi-fluid modelling will enable mass transport by convection but the approach means a whole new atmospheric model rather than a stand alone routine that can be incorporated into an existing model. This paper provides some closures necessary for multi-fluid modelling and \change[HW]{validation}{evaluation} of the technique for two dimensional dry convection.

@@

\add[HW]{
\protect\citeA{LR01} introduced the ``assumed-distribution higher-order closure'' (ADHOC) parameterisation of the boundary layer and convection which solves prognostic equations for higher-order moments of the sub-grid-scale flow, such as the triple correlation of the vertical velocity anomalies, and diagnoses updraft and downdraft means from the higher-order moments. Thus all necessary statistics can be calculated from the grid-box-mean values that are predicted by the dynamical core. Net mass transport by convection is included because it is part of the grid-box-mean. ADHOC was extended by \protect\citeA{GLC02} to use bi-Gaussian probability distribution functions (PDFs) rather than top-hat distributions to represent sub-grid-scale variability. This formed the basis of the ``Cloud Layers Unified By Binormals'' (CLUBB) parameterization \protect\cite<>{LSW+12} which was first used at grey zone resolutions.}

\citeA{TWV+18} proposed multi-fluid modelling of convection in order
to treat non-equilibrium and net mass transport \remove[HW]{correctly and} consistently.
\change{with}{This involves using} the same numerics and physics to \change[HW]{control thermals}{prognose properties of separate parts of the fluid, for example updrafts}, the stable environment and downdrafts \remove[HW]{dynamics}. \citeA{Yano14} derived similar
equations \remove[HW]{for multiple segments} and showed how this is a generalisation
of the mass-flux formulation. The \citeA{TKP+18} ``extended eddy
diffusivity mass flux'' or extended EDMF scheme also uses similar
equations but \citeA{TKP+18}
\change[HW]{didn't propose a suitable numerical method for solving the equations.}
{only solve the equations in a single column without coupling to the continuity equation of a dynamical core.}
\change[HW]{Multi-fluids promises big improvements
in the representation of sub-grid-scale convection and unification
with the representation of turbulence, particularly at the grey zone.
However, there is a long way to go, particularly as}
{The multi-fluids approach has an advantage over ADHOC and CLUBB in solving prognostic equations for first-order moments (means of eg. updraft and environment) directly rather than solving prognostic equations for higher-order moments of the whole fluid in order to diagnose means of updrafts and the environment. Solving directly for sub-fluid means should be less sensitive to closure assumptions. However} multi-fluids require
a dedicated model rather than being a stand alone parameterisation
for a dynamical core. \citeA{TEB19} and \citeA{WM19} presented solutions
of the multi-fluid equations assuming two fluids that share the same
pressure. \remove[HW]{(or that pressure differences are predominantly due to drag
between the fluids)}. \citeA{TEB19} showed that these equations \remove[HW]{(without
drag)} are in fact unstable and can be stabilised by diffusion of vertical
velocity whereas \citeA{WM19} stabilised the equations with diffusion
and drag between fluids. Neither of these stabilisation techniques
are acceptable;
\add[HW]{sufficient diffusion to stabilise the multi-fluid equations may smooth out real features of the flow and the diffusion between fluids and drag used by \protect\citeA{WM19} meant that both fluids tended to move together rather than through each other.}
In this paper we show that there are significant
and sustained pressure differences between the fluids (section \ref{sec:results}) \add[HW]{and that the use of separate pressures stabilises the equations}.

@@

Many of the challenges of representing convection with the multi-fluid
Navier-Stokes equations \cite<e.g. those described in>{WM19} carry
over to the Boussinesq equations \add[HW]{because} convection is buoyancy dominated
and close to incompressible. The resolved test cases presented in
section \ref{sec:results} give very similar results for Navier-Stokes
and Buossinesq equations. Therefore for simplicity we focus on the
\remove[HW]{multi-fluid} Boussinesq equations without background stratification:
\note[HW]{This is additional material until the start of 2.1}
\begin{eqnarray}
\frac{\partial \mathbf{u}}{\partial t} + \nabla\cdot(\mathbf{u}\mathbf{u})
+\nabla P & = & b \mathbf{k}+\nu\nabla^{2}\mathbf{u}
\label{eq:singleMom}
\\
\frac{\partial b}{\partial t} + \nabla\cdot(\mathbf{u}b)
 & = & \alpha\nabla^{2}b
\label{eq:singleb}
\\
\nabla\cdot\mathbf{u} & = & 0
\label{eq:singleDivFree}
\end{eqnarray}
where variables are defined in table \ref{tab:defns}.

@@

The single-fluid Boussinesq equations will be conditionally averaged following \citeA{TWV+18} to give the multi-fluid Boussinesq equations. Lagrangian labels for each fluid $i$ are defined as $I_i=1$ in fluid $i$ and zero elsewhere. In this paper, $I_0$ labels sinking and $w=0$ fluid and $I_1$ labels rising fluid. $I_i$ satisfies:
\begin{equation}
\frac{DI_i}{Dt}=0.
\label{eq:LagrangianLabel}
\end{equation}
Applying conditional volume average to $I_i$ we define the volume fraction of fluid $i$ and the velocity and buoyancy of fluid $i$:
\begin{eqnarray}
\sigma_i &=& \overline{I_i} \\
\sigma_i \mathbf{u}_i &=& \overline{I_i \mathbf{u}} \\
\sigma_i b_i &=& \overline{I_i b}
\label{eq:defineFluidFields}
\end{eqnarray}
which implies
\begin{equation}
\sum_{i}\sigma_{i}  =  1.
\label{eq:sumOne}
\end{equation}
As we are considering the Boussinesq equations we assume that variations in density only affect the buoyancy terms so $\mathbf{u}_i$ and $b_i$ are defined without density weighting.

@@

Eqns (\ref{eq:momFlux}) and (\ref{eq:bFlux}) are solved in advective form in which the mass transfer terms are more complicated due to the mass transfer terms in \ref{eq:sigma}:
\begin{eqnarray}
\frac{D_{i}\mathbf{u}_{i}}{Dt}+\nabla P_{i}
& = &
b_{i}\mathbf{k}+\nu\nabla^{2}\mathbf{u}_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(\mathbf{u}_{ji}^{T}-\mathbf{u}_{i}\right)-S_{ij}(\mathbf{u}_{ij}^{T}-\mathbf{u}_{i})-\mathbf{D}_{ij}\right\}
\label{eq:mom}\\
\frac{D_{i}b_{i}}{Dt}
& = &
\alpha\nabla^{2}b_{i}+\sum_{j\ne i}\left\{ \frac{\sigma_{j}}{\sigma_{i}}S_{ji}\left(b_{ji}^{T}-b_{i}\right)-S_{ij}\left(b_{ij}^{T}-b_{i}\right)\right\} \label{eq:b}
\end{eqnarray}
where $D_{i}\big/Dt=\partial/\partial t+\mathbf{u}_{i}\cdot\nabla$ is the total derivative with respect to fluid $i$,

@@

\citeA{TEB19} and \citeA{WM19} assumed that each \remove[HW]{co-located} fluid
shared the same pressure \change[HW]{leading}{field. This lead} to unstable equations that \citeA{TEB19}
stabilised using diffusion of vertical velocity and \citeA{WM19}
stabilised using mass exchanges or drag between the fluids. \citeA{TEB19}
achieved realistic results in \change[HW]{single}{one} column experiments of \add[HW]{the} convective
boundary layer but the amount of diffusion needed would spoil simulations
in the free troposphere \add[HW]{by diffusing real features as well as spurious artifacts}. The stabilisation used by \citeA{WM19} meant
that the two fluids tended to move as one which defeats the purpose
of using multi-fluid modelling.

@@

We will assume that pressure in each fluid is given by a \remove[HW]{parameterised}
perturbation, $p_{i}$, from the total pressure, $P$:
\begin{equation}
P_{i}=P+p_{i}.
\end{equation}
\add[HW]{In order to derive a suitable form of parameterisation for $p_i$ we will first consider the} \citeA{BN86} \add{model.}

@@

The different fluids may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}.
In fact, the most buoyant air should be transferred from fluid 0 to
fluid 1 and vice versa, and the air with least downward momentum should
be transferred from 0 to 1 and vice versa. The properties of the fluids
transferred should depend on the modelling of \change[HW]{sub-grid-scale}{sub-filter-scale} variability \add[HW]{(i.e. the variability within each fluid)}
which is beyond the scope of this paper. In section \ref{sec:results}
we conditionally average high resolution solutions based on the sign
of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
Therefore the air that is transferred at the interface will have $w=0$.
For two dimensional multi-fluid simulations we assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from. Therefore
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
For buoyancy, following \citeA{TEB19}, we use:
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
\end{equation}
and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
\add[HW]{
$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<eg.>{AK67,AS74}.
}
Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is loosing mass (as demonstrated in section \ref{sec:results}).

@@

\section{Numerical \change[HW]{Solution}{Method} \label{sec:numerics}}

@@

\section{\change[HW]{Validation}{Evaluation} Test Cases\label{sec:results}}

Two test cases are developed to tune parameters and to \change[HW]{validate}{evaluate} the
use of multi-fluid equations to represent dry, two-dimensional, sub-grid-scale
convection. The first is transient; the standard rising bubble of
\citeA{BF02}. \remove{We aim to reproduce the vertical heat transport, the
mean velocity of the rising air, the bouyancy of the rising air and
pressure differences between two fluids in a single column two fluid
model.} The second \remove[HW]{test case} is steady state with heat transfer at
the ground and uniform radiative cooling \add[HW]{(radiative convective equilibrium)}. For both test cases, the
reference solution is a single-fluid solution of the two-dimensional
Boussinesq equations at high horizontal and vertical resolution. \add[HW]{This will be compared with the two-fluid model run using one column. We aim to reproduce the vertical heat transport, the mean velocity of the rising air, the bouyancy of the rising air and the pressure differences between fluids in one column two-fluid model.}

@@

Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
Three values of $\gamma$ are tested. $\gamma$ is set from equation
(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
radius and a buoyancy scale equal to the initial maximum buoyancy
to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
the velocity profile too smooth and the updraft too weak so the
bubble does not rise enough. It is reasonable to consider smaller
values of $\gamma$ because the buoyancy does not retain its initial
maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
leads to the leading edge of the bubble rising too quickly. Smaller
values of $\gamma$ leave a discontinuity in the updraft velocity
at the leading edge of the bubble and larger values of $\gamma$ reduce
the velocity further, meaning that the bubble does not rise enough
(not shown). None of the values of $\gamma$ reproduce the peak updraft
velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
meaning that the bubble rise and $\sigma_{1}$ are approximately correct
and pressure increases above the centre of the bubble are realisitic.
The large low pressure at the bottom of the bubble is not reproduced.
This is located at the lobes of the highest buoyancy in the resolved
simulation (figure \ref{fig:bubble}). It would be tempting to model
this by assuming hydrostatic pressure or the Bernouilli equation,
but these are both forms of the momentum equation which is used to
calculate the velocity and so cannot also be used to model the pressure.

The results in the top row of figure \ref{fig:multiFluidSingleColumn}
use $\gamma=-10^{4}$ and $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ but
this time with drag set by $C_{D}/r_{c}=1/2000\text{m}^{-1}$. The
drag slows the updrafts without increasing the mixing between the
fluids which makes the solutions less like the resolved simulations.
Although drag is known to be an important term in the momentum equations
for buoyant thermals and plumes \cite<e.g.,>{RC15}, the drag is related
to mixing with downdraft air which is accounted for in the entrainment
term of the momentum equation. So adding a separate term from drag
risks double counting and slows the plume too much.

@@

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
This combination produces smooth solutions but the updraft is too
weak and too much is entrained into fluid 1. Using this entrainment,
the updraft will entrain more and more air until $\sigma_{1}=1$.
The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
entrainment and detrainment for this test case using conditional averaging
based on $w$.

Two alternative models for estimating the buoyancy of the fluid transferred
between updraft and downdraft have been tested. The results in
the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraft),
the mean buoyancy of fluid one increases. This leads to very high
buoyancy in fluid one which is not present in the resolved simulation.
The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. This again leads to very
large buoyancy in fluid one and also negative buoyancy in fluid zero
which should not occur for this test case. These simple models reinforce
the idea that the buoyancy of the fluid transferred should depend
on knowledge of sub-grid-scale variability of $b$ within each fluid
\textendash{} these simple assumptions can lead to unrealistic behaviour.
The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
fluid transferred takes the mean properties with it.

This section has demonstrated the value of using \change[HW]{single}{one} column,
multi-fluid model to simulate a buoyant rising bubble with a single
updraft fluid and a single downdraft fluid. Transfers between
the fluids have been successfully modelled using entrainment set by
divergence giving realistic updraft fractions. Entrainment calculated
as the reciprocal of plume width was not successful. The pressure
difference between the fluids has also been represented by divergence
with a coefficient close to that expected from dimensional analysis.
Including drag between the fluids did not improve simulations. Two
models of transferring non-mean properties between fluids were tested
but neither was plausible. There are clearly discrepancies between
the single-fluid resolved rising bubble and the two fluid \change[HW]{single}{one} column
rising bubble but we do not want to over fit the multi-fluid model
to one, dry, two dimensional test case.

@@

This test case is designed to have strong updrafts in narrow plumes
and weak descent elsewhere to mimic atmospheric convection but without
the complication of moisture, phase changes and three spatial dimensions.
A snapshot of the buoyancy, vertical velocity and pressure of the
radiative-convective equilibrium test case at $2\times10^{5}\text{s}$
are shown in figure \ref{fig:RCE_resolved} showing intense, narrow
updrafts. The buoyant air at the ground rises in narrow plumes,
accelerating due to buoyancy and pressure gradients then decelerating
due to pressure gradients before reaching the top. The plumes spread
out and the sinking air is a mixture of warm and cold with similar
pressure gradients in the rising and falling air, accelerating then
decelerating the flow so as to maintain continuity.

@@

This paper presents solutions of the multi-fluid Boussinesq equations
for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution. Two test cases are used to \change[HW]{validate}{evaluate}
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are conditionally averaged based on the sign
of vertical velocity ($w$) in order to create rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.
